Cyclone: Replication Middleware for NVM Clusters

### 2016-09-14 paper/paper.tex
Added list of graphs.

\subsection{Checkpoints}

\section{Evaluation}

>>>>

\section{Evaluation}
\begin{figure}
  Source: results_raw.csv. X-axis throughput (Mops/sec). Y-axis latency. Fix
  ports = 4. Fix payload = 0. One line per number of replicas (1,2,3).
  \caption{Replicaton Performance - Varying replica count}
  \label{fig:perf_rep}
\end{figure}

\begin{figure}
  Source: results_raw.csv. X-axis throughput (Mops/sec). Y-axis latency. Fix
  replicas = 3. Fix payload = 0. One line per number of ports.
  \caption{Replicaton Performance - Varying ethernet ports}
  \label{fig:perf_ports}
\end{figure}

\begin{figure}
  Source: results_raw.csv. Fix replicas = 3. Set of 4 graphs. One graph for each
  port count (1,2,3,4). X-axis throughput (Gbps). Y-axis latency. One line per
  payload size.
  \caption{Replicaton Performance - Varying payload size}
  \label{fig:perf_payload}
\end{figure}

\begin{figure}
  Source: results_clwb.csv. Bar graph with 3 groups of bars - one group for
  payload = 0, one group for payload = 190, one for 512. Each group has 3 bars -
  one for window =1, one for window = 10, one for window = 10000 (infty)
  \caption{Replicaton Performance - CLFLUSH window}
  \label{fig:perf_clflush}
\end{figure}

\begin{figure}
  Source: results_quorum.csv. X-axis throughput (Mops/sec). Y-axis latency. Fix
  replicas = 3. Fix payload = 0. One line for each of ports = 1,2,3,4.
  \caption{Replicaton Performance - quorum count}
  \label{fig:perf_quorums}
\end{figure}

\begin{figure}
  Source: results_cc.csv.Fix replicas = 3. X-axis is throughput
  (Mops/sec). Y-axis is Latency. One line for each of ports = 1,2,3,4.
  \caption{Crash consistency overheads}
  \label{fig:perf_cc}
\end{figure}

\begin{figure}
  Source: results_app.csv. X-axis is throughput
  (Mops/sec). Y-axis is Latency. One line for each of read_fraction = 0, 50, 100
  \caption{Hash Table Performance}
  \label{fig:perf_app}
\end{figure}
